
---
output: github_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# dictionary <a href='https://github.com/stevecondylios/dictionary'></a>


<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/dictionary)](https://cran.r-project.org/package=dictionary)
<!-- badges: end -->

`dictionary` gives the ability to get the dictionary definition, phonetics, and origin of English words. 


### Installation

Installation via CRAN `install.packages("dictionary")`

```{r message=FALSE, eval = FALSE}

install.packages("dictionary")

``` 


Get dictionary definition of "hello"

```{r message=FALSE}

library(dictionary)
hello <- define("hello")

``` 


View a word's **part(s) of speech** and **definition(s)**:

```{r}
hello$meanings
```


View a word's **phonetic**:


```{r}
hello$phonetic
```


Hear a word's **pronunciation**:

```{r}

hello$phonetics

```

To hear the word pronounced out loud, visit the provided url(s): https://ssl.gstatic.com/dictionary/static/sounds/20200429/hello--_gb_1.mp3











